02_DESeq_hyp

### 2019-04-06 analysis/02_DESeq2_hyp.Rmd
better gridplot

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00")
```

>>>>

dat$V1 <- factor(dat$V1, levels = 
                              c("control", "bldg", "lay", "inc.d3", "inc.d9", 
                                "inc.d17", "hatch", "n5", "n9"))
dat$V2 <- factor(dat$V2, levels = 
                              c("control", "bldg", "lay", "inc.d3", "inc.d9", 
                                "inc.d17", "hatch", "n5", "n9"))

ggplot(dat, aes(V1, V2)) +
  geom_tile(aes(fill = V3)) +
  scale_fill_viridis(na.value="#FFFFFF00") + 
  xlab("Treatment") + ylab("Treatment") +
  labs(fill = "# of DEGs")
```
